Providing better confidentiality and authentication on the Internet using Namecoin and MinimaLT

### 2014-01-06 paper.tex
NMC / zooko

Writing data in the blockchain does have a certain price. Registering a domain does cost the registration fee (0.01NC that goes to nobody) plus the transaction fee (that goes to the miner who succeeds in adding the block that contains this transaction).

The cost includes a network fee and a transaction fee. The fees are denominated in Namecoins (\emph{NC}). Initially, the network fee was 50 NC but it decreases twice every 2 months, which means that it is already less than 1 NC after a year. This design was meant to make it expensive to register domains in the first few months to avoid the issue of domain name squatting.

@@

This would make my website accessible at the \emph{fredericjacobs.bit} address!

>>>>

Writing data in the blockchain does have a certain price. Registering a domain does cost the registration fee (0.01NMC that goes to nobody) plus the transaction fee (that goes to the miner who succeeds in adding the block that contains this transaction).

The cost includes a network fee and a transaction fee. The fees are denominated in Namecoins (\emph{NMC}). Initially, the network fee was 50 NMC but it decreases twice every 2 months, which means that it is already less than 1 NMC after a year. This design was meant to make it expensive to register domains in the first few months to avoid the issue of domain name squatting.

@@

This would make my website accessible at the \emph{fredericjacobs.bit}, a memorable, secure (a client can verify the fingerprint) and global address, the triangle has been squared!
